\section{Limited Solar-BESS Model v4}
In this model, the solar capacity is limited, either due to a pre-installed capacity
or there is no more area available to install panels. Grid power is available.

\paragraph{Assumptions}
\begin{enumerate}
    \item The solar capacity is limited to $C_{\text{solar}}$ kWh, 
    \begin{equation}
        C_{\text{solar}} = \varepsilon_{\text{s}} \, E_{\text{load}}. 
    \end{equation}
    where $\varepsilon_{\text{s}}$ is the fraction of the daily energy load
    $E_{\text{load}}$ provided by solar power. 

    \item The total daily load is divided into peak and normal load during day and night
    times as in the previous models.
    \begin{equation}
    E_{\text{load}}  = P_{\text{p}} T_{\text{p}} 
    + P_{\text{n}} T_{\text{nd}} + P_\text{n} T_\text{nn} 
    + P_\text{idle} T_\text{idle}
    \end{equation}

 
    \item During peak hours, BESS and solar provide the power to the load.
    \item During normal hours, BESS is charged using solar power and grid power.
    
\end{enumerate}

\paragraph{Model} The capacity of the BESS is the same as in Model v1, in that it has to support
the load demand during peak hours (occurring twice a day). 
\begin{equation}
    C_{\text{v4}} = \frac{P_{\text{p}} T_{\text{p}} }{2 \eta}.
\end{equation}
The daily electricity bill is
\begin{align}
    B_{\text{v4}} & = 
       R_{\text{s}} C_{\text{solar}} \frac{T_{\text{p}}/2}{T_\text{s}} \quad \text{(peak, day)}  \\
    & + R_{\text{s}} C_{\text{solar}} \frac{T_{\text{nd}}}{T_\text{s}} 
    + R_{\text{n}} \left[ (P_{\text{n}} T_{\text{nd}} - C_{\text{solar}}) + C \right] 
     \quad \text{(normal, day)} \\
     & + 0 \quad \text{(peak, night)} \\
     & + R_{\text{n}} \left[ P_{\text{n}} T_{\text{nn}} + C \right] \quad \text{(normal, night)} \\
     & + 0 \quad \text{(idle)} \\
     & = R_{\text{s}} C_{\text{solar}} + R_{\text{n}} \left[ P_{\text{n}} T_{\text{n}} 
     - C_{\text{solar}} + 2 C \right] \\
     & = (R_{\text{s}}-R_{\text{n}}) \, C_{\text{solar}}  + R_{\text{n}} 
     \left[ P_{\text{n}} T_{\text{n}}  + 2 C \right].
\end{align}
Notes: 
\begin{enumerate}
\item The first term in the first line represents the cost of the fraction of
the daily solar energy used during the day time peak-rate period (towards the load demand).  The
remaining load demand is met by the BESS (for which there is no cost).

\item The first term in the second line represents the balance fraction of the solar power used
for during the normal-rate period.

\item The second term in the second line represents the cost of the normal-rate grid power 
used to meet the balance of the normal-rate load and to charge the BESS.

\item During normal-rate day time, it does not matter
if the BESS is being charged by solar or grid power. The combined demand of the
BESS and the load is met jointly by solar and grid power. That is the reason
the term $R_{\text{s}} C_{\text{solar}}$ appears as a single term after
simplification.  

\item A simplification of $T_{\text{n}} = T_{\text{nd}} + T_{\text{nn}}$, the total normal-rate duration, has been used.

\end{enumerate}

%% Local Variables:
%%% mode: latex
%%% TeX-master: "paybackPeriod"
%%% End:
